\paperTitle

### 2014-01-31 doc/icml2014/directed.tex
Minor changes - Added note on experiment, etc.

  Let $x_v$ be an observed variable with parents $P$ and children $C$.
  Consider the following transformation.
  Replace $x_v$ with a new hidden variable \hp\ with the same
  parents $\Pa(x_v)$ and children $\text{Ch}(x_v) \union \{x_{v_1}, x_{v_2}, x_{v_3}\}$,
  where $x_{v_1},x_{v_2},x_{v_3}$ are three copies of $x$
  (\figureref{reduction}). 
  The domain of $\hp$ is the same as $x$,
    and $\mOpp{v}{\textrm{new}} = I$.\footnote{Though we have assumed that all hidden variables share the
      same domain, $[k]$, our work generalizes to hidden domains of
      different sizes, provided \assumptionref{full-rank-plus} is satisfied.
      }

@@

% DONE: move here because not central to story
\paragraph{Remark.} We note that \propertyref{bottleneck} can be relaxed if some cliques
  share parameters.
In the directed grid model, we can identify the conditional moments $O$ from just
  $x^a_1, x^b_1$ and $x^a_2$.
  Therefore, we do not require that $h_2, h_3$ or $h_4$
  be bottlenecks, and can omit the observations $x^b_2, x^b_3$ and $x^b_4$.
  \todo{make this a footnote if running out of space}
% PL: don't understand this comment
%In this case, we only require that the hidden variables in distinct
  %cliques share parameters.

@@

To apply $\TensorFactorize$, we need that each $\mOpp{v}{i}$ has full
  column rank and that $\pi^{(i)} \eqdef \Pr(h_i) \succ 0$.
But $\mOpp{v}{i}$ is a product of
tensors on the path from $h_i$ to $x_v$, marginalizing out the rest of the graph.
To make this property more interpretable, let us assume the following property:\verify
\begin{assumption} 
\label{asm:full-rank-plus}
For every clique $\sC \in \sG$ (including ones involving observed variables),
every slice of the marginals $Z_\sC$ has full column rank $k$.
\end{assumption}
In our directed grid example (\sectionref{directedExample}), for the clique $\sC = \{ h_1, h_2 \}$ this
  condition implies $\pi = \bP(h_1) \succ 0$ and $T = \bP(h_2 \mid h_1)$ has column rank $k$; 
for the clique $\sC = \{ h_1, x_1 \}$, it implies $O = \bP(x_1 \mid h_1)$ has column rank $k$

>>>>

  Let $x_v$ be an observed variable with parents $P$ and children $C$.
  Consider the following transformation.
  Replace $x_v$ with a new hidden variable \hp\ with the same
  parents $\Pa(x_v)$ and children $\text{Ch}(x_v) \union \{x_{v_1}, x_{v_2}, x_{v_3}\}$,
  where $x_{v_1},x_{v_2},x_{v_3}$ are three copies of $x$
  (\figureref{reduction}). 
  The domain of $\hp$ is the same as $x$,
    and $\mOpp{v}{\textrm{new}} = I$.\footnote{
      Though we have assumed that all hidden variables share the
      same domain, $[k]$, our work generalizes to hidden domains of
      different sizes, provided \assumptionref{full-rank-plus} is satisfied.
      }

@@

% DONE: move here because not central to story
\paragraph{Remark.} We note that \propertyref{bottleneck} can be relaxed if some cliques
  share parameters.
In the directed grid model, we can identify the conditional moments $O$ from just
  $x^a_1, x^b_1$ and $x^a_2$.
  Therefore, we do not require that $h_2, h_3$ or $h_4$
  be bottlenecks, and can omit the observations $x^b_2, x^b_3$ and $x^b_4$.
%  \todo{make this a footnote if running out of space}
% PL: don't understand this comment
%In this case, we only require that the hidden variables in distinct
  %cliques share parameters.

@@

To apply $\TensorFactorize$, we need that each $\mOpp{v}{i}$ has full
  column rank and that $\pi^{(i)} \eqdef \Pr(h_i) \succ 0$.
But $\mOpp{v}{i}$ is a product of
tensors on the path from $h_i$ to $x_v$, marginalizing out the rest of the graph.
To make this property more interpretable, let us assume the following property:%\verify
\begin{assumption} 
\label{asm:full-rank-plus}
For every clique $\sC \in \sG$ (including ones involving observed variables),
every slice of the marginals $Z_\sC$ has full column rank $k$.
\end{assumption}
In our directed grid example (\sectionref{directedExample}), for the clique $\sC = \{ h_1, h_2 \}$ this
  condition implies $\pi = \bP(h_1) \succ 0$ and $T = \bP(h_2 \mid h_1)$ has column rank $k$; 
for the clique $\sC = \{ h_1, x_1 \}$, it implies $O = \bP(x_1 \mid h_1)$ has column rank $k$
